Treebeard : An Optimizing Compiler for Decision Tree Based ML Inference

### 2022-04-25 docs/MICRO 2022/MIR.tex
Micro paper (#37)
* Add results for multiple batch sizes run

* Changes to benchmark code

* Add xgboost and treelite compare results

* Add AMD results

* Add parallel performance results

* code to generate graphs + modified result numbers

* Fix bug in plotting code

* Add grid to line graphs

* Add grid lines

* Add results for varying number of cores

* Run parallel tests

* Add AMD parallel results

* Update graph generator

* Add scaling results for AMD

* Fix images, alter font sizes and axes

* Just use Probability based tiling

* Update images - Change axis font size, fix wrong graph

\subsection{Tree Walk Interleaving}
A key bottleneck we found when we profiled code generated from tiled walks (even after vectorization) was that true dependencies between instructions were still causing
a significant number of processor stalls. Performing a walk with a single input-tree pair was not providing enough independent instructions to keep the processor busy. In order to address this \Treebeard{} applies an unroll and jam transformation on the inner most loops of the loop nest. This has 
the effect of walking multiple tree and input row pairs in an interleaved fashion. 
This mitigates the dependency stalls by enabling scheduling of instructions from independent tree walks.

This optimization is performed in two steps. 
First a pass on the mid-level IR transforms the loop structure. 
The following listing shows the mid-level IR when the inner loop over the input rows is unrolled 
by a factor of 2 and the two resulting tree walks are jammed together.

\begin{lstlisting}[style=c++]
  forest = ensemble(...)
  for t = 0 to numTrees step 1 {
    for i = 0 to batchSize step 2 {
      tree = getTree(forest, t)
      pred1, pred2 = InterleavedWalk((tree, rows[i]), (tree, rows[i+1]))
    }
  }
\end{lstlisting}
Next when lowering, the operations to traverse each of the tree, input row pairs 
(the arguments to the \texttt{InterleavedWalk}) are interleaved. One step of the interleaved 
walk is listed below. 
\begin{lstlisting}[style=c++]
  // ... 
  n1 = n2 = getRoot(tree)
  // ...
  threshold1 = loadThresholds(n1)
  threshold2 = loadThresholds(n2)
  featureIndex1 = loadFeatureIndices(n1)
  featureIndex2 = loadFeatureIndices(n2)
  feature1 = rows[i][featureIndex1]
  feature2 = rows[i][featureIndex2]
  pred1 = feature1 < threshold1
  pred2 = feature2 < threshold2
  n1 = getChildNode(n1, pred1)
  n2 = getChildNode(n2, pred2)
  // ...
\end{lstlisting}

\CommentOut{
These transformations are fairly general and are not aware of the in memory representation of the model. Therefore, they 
are reusable across different in memory representations - the ones that are currently built into Treebeard or ones that 
maybe added in the future.
\TODO{AP I feel the way this section is currently written makes the optimization seem extremely trivial. Is there a different 
way to present it?}
}
\subsection{Loop Peeling and Walk Unrolling}
\Treebeard{} splits the loop that performs a tree walk into two parts. As can be made aware (through a simple pass on the IR) of the depth of the first leaf in a tree, it peels and introduces a \op{prologue} loop that walks down the tree a constant number of steps (for example, up to the depth of the first leaf) and then performs the rest of the tree walk in a separate loop.
% Next \Treebeard{} unrolls the prologue completely, avoiding all traversal induced branching in it.

Several rewrites of the peeled loop are possible. \Treebeard{} completely unrolls the prologue if the peeled loop 
walks the tree upto the depth of the first leaf. In cases where \Treebeard{} has already padded and balanced the 
tree (Section~\ref{sec:treeorder}), walk unrolling completely avoids all traversal induced branching. In the case of 
probability based tiling, the prologue loop enables specialization of leaf checks so that these checks 
are faster (and less general) for the most probable leaves.

@@

\subsection{Parallelization}
Currently, \Treebeard{} performs a na\"ive parallelization of the inference computation. When parallelism is enabled, the 
loop over the input rows is parallelized using a \op{parallel.for} construct in MLIR. Treebeard rewrites 
the mid-level IR by tiling the loop over the input rows with a tile size equal to the number of cores. 
As a concrete example, consider the case where we intend to perform inference using a model with 4 trees 
on a batch of 64 rows. Further, assume that we wish to parallelize this computation across 8 cores. 
\Treebeard{} then generates the following IR.
\begin{lstlisting}[style=c++]
  forest = ensemble(...)
  parallel.for i0 = 0 to 64 step 8 {
    for i1 = 0 to 8 step 1 {
      i = i0 + i1
      prediction = 0
      for t = 0 to 4 step 1 {
        tree = getTree(forest, t) 
        treePrediction = WalkDecisionTree(tree, rows[i])
        prediction = prediction + treePrediction
      }
      predictions[i] = prediction
    }
  }
\end{lstlisting}
Currently, \Treebeard{} does not perform other standard parallelization optimizations  (such as loop tiling) as they
are generic and independent of the problem domain. We leave a more thorough exploration of parallelizing decision trees
to future work.

>>>>

\section{Optimizations on mid-level IR}
\label{Sec:MIR}
In this section, we present various tree walk optimizations performed by
\Treebeard{} on the mid-level IR.

\subsection{Tree Walk Interleaving}
A key bottleneck we found when we profiled code generated from tiled walks (even 
after vectorization) was that true dependencies between instructions were still 
causing a significant number of processor stalls. Performing a walk with a 
single input-tree pair did not provide enough independent instructions to keep 
the processor busy. In order to address this, \Treebeard{} applies an 
unroll-and-jam transformation on the innermost loops of the loop nest. This has 
the effect of walking multiple tree and input row pairs in an interleaved 
fashion.  This mitigates the dependency stalls by enabling scheduling of 
instructions from independent tree walks.

This optimization is performed in two steps. First, a pass on the mid-level IR 
transforms the loop structure.  It unrolls the innermost loops of the loop nest 
a specified number of times and jams together tree walks from the different 
iterations.  The following listing shows the mid-level IR when the inner loop 
over the input rows is unrolled by a factor of two and the two resulting tree 
walks are jammed together.

\begin{lstlisting}[style=c++]
  for t = 0 to numTrees step 1 {
    for i = 0 to batchSize step 2 {
      tree = getTree(forest, t)
      pred1, pred2 = InterleavedWalk((tree, rows[i]),
                                     (tree, rows[i+1]))
    }
  }
\end{lstlisting}
Next when lowering, the operations to traverse each of the tree, input row pairs 
(the arguments to the \texttt{InterleavedWalk}) are interleaved. One step of the interleaved 
walk is listed below. 
\begin{lstlisting}[style=c++]
  // ... 
  tile1 = tile2 = getRoot(tree)
  // ...
  threshold1 = loadThresholds(tree, tile1)
  threshold2 = loadThresholds(tree, tile2)
  featureIndex1 = loadFeatureIndices(tree, tile1)
  featureIndex2 = loadFeatureIndices(tree, tile2)
  feature1 = rows[i][featureIndex1]
  feature2 = rows[i][featureIndex2]
  pred1 = feature1 < threshold1
  pred2 = feature2 < threshold2
  tile1 = getChildTile(tile1, pred1)
  tile2 = getChildTile(tile2, pred2)
  // ...
\end{lstlisting}

\CommentOut{
These transformations are fairly general and are not aware of the in-memory representation of the model. Therefore, they 
are reusable across different in-memory representations - the ones that are currently built into Treebeard or ones that 
maybe added in the future.
\TODO{AP I feel the way this section is currently written makes the optimization seem extremely trivial. Is there a different 
way to present it?}
}
\subsection{Tree Walk Peeling and Tree Walk Unrolling}
\Treebeard{} splits the loop that performs a tree walk into two parts. It peels 
and introduces a \op{prologue} loop that walks down the tree a constant number 
of steps (for example, up to the depth of the first leaf) and then performs the 
rest of the tree walk in a separate loop.

%% As can be made aware (through a simple pass on the IR) of the depth of the first leaf in a tree, 
%First it identifies the leaf with the minimum depth through a simple pass.  Then

% Next \Treebeard{} unrolls the prologue completely, avoiding all traversal induced branching in it.

Several rewrites of the peeled loop are possible. \Treebeard{} completely 
unrolls the prologue if the peeled loop walks the tree upto the depth of the 
first leaf. In cases where \Treebeard{} has already padded and balanced the tree 
(Section~\ref{sec:treeorder}), unrolling the prologue loop completely avoids all 
traversal induced branching.  In the case of probability-based tiling, the 
prologue loop enables specialization of leaf checks so that these checks are 
faster (and less general) for the most probable leaves.

@@

\subsection{Parallelization}
Currently, \Treebeard{} performs a na\"ive parallelization of the inference computation. When parallelism is enabled, the 
loop over the input rows is parallelized using MLIR's OpenMP support. \Treebeard{} rewrites 
the mid-level IR by tiling the loop over the input rows with a tile size equal to the number of cores. 
As a concrete example, consider the case where we intend to perform inference 
using a model with four trees on a batch of 64 rows. Further, assume that we 
wish to parallelize this computation across 8 cores.  \Treebeard{} then 
generates the following IR:
\begin{lstlisting}[style=c++]
  parallel.for i0 = 0 to 64 step 8 {
    for i1 = 0 to 8 step 1 {
      i = i0 + i1
      prediction = 0
      for t = 0 to 4 step 1 {
        tree = getTree(forest, t) 
        treePrediction = WalkDecisionTree(tree, rows[i])
        prediction = prediction + treePrediction
      }
      predictions[i] = prediction
    }
  }
\end{lstlisting}
Currently, \Treebeard{} does not perform other standard parallelization 
optimizations as they are generic and independent of the 
problem domain. We leave a more thorough exploration of parallelizing decision 
trees to future work.

### 2022-04-25 docs/MICRO 2022/abstract.tex
Micro paper (#37)
* Add results for multiple batch sizes run

* Changes to benchmark code

* Add xgboost and treelite compare results

* Add AMD results

* Add parallel performance results

* code to generate graphs + modified result numbers

* Fix bug in plotting code

* Add grid to line graphs

* Add grid lines

* Add results for varying number of cores

* Run parallel tests

* Add AMD parallel results

* Update graph generator

* Add scaling results for AMD

* Fix images, alter font sizes and axes

* Just use Probability based tiling

* Update images - Change axis font size, fix wrong graph

\begin{abstract}
  Decision tree ensembles are a commonly used machine learning model
  generated by machine learning techniques like gradient boosting and random
  forests. These models are used in applications ranging from recommendation systems
  to tabular data analysis and are also deployed at scale in the enterprise.
  Several libraries such as XGBoost, LightGBM, and Sklearn expose algorithms for both
  training and inference with decision tree ensembles. These systems incorporate a
  limited set of optimizations usually targeted at specific hardware. Further, existing
  systems do not specialize the inference code to the model being used.

  This paper presents Treebeard, an extensible compiler for decision tree models.
  Treebeard progressively lowers inference code to LLVM IR through multiple intermediate
  representations. By applying model specific optimizations at the higher levels, loop
  optimizations at the middle level, and machine specific optimizations lower down,
  Treebeard can specialize inference code for each model on each supported
  hardware target. To improve model inference performance, Treebeard performs several 
  novel optimizations such as tree tiling, tree walk unrolling, and tree walk interleaving.

  We implement Treebeard using the MLIR compiler infrastructure and
  demonstrate the utility of Treebeard by evaluating it on a diverse set of
  tree ensemble models. We report that Treebeard optimizations improve
  average latency over a batch of inputs by 2.2X compared to an unoptimized baseline.
  Further, we find that Treebeard is significantly faster than other frameworks like
  XGBoost  (3X on average) and Treelite (5X on average) in both single and multi-core
  settings.
\end{abstract}

>>>>

\begin{abstract}
  Decision tree ensembles are among the most commonly used machine learning
  models. These models are used in a wide range of applications and are deployed
  at scale. Inference with decision tree ensembles is usually performed with
  libraries such as XGBoost, LightGBM, and Sklearn. These libraries incorporate
  a fixed set of optimizations for the hardware targets they support. However,
  maintaining these optimizations is prohibitively expensive with the evolution
  of hardware.  Further, they do not specialize the inference
  code to the model being used, leaving significant performance on the table.

  This paper presents \Treebeard{}, an optimizing compiler that progressively
  lowers  inference code to LLVM IR through multiple intermediate abstractions.
  By applying model-specific optimizations at the higher levels, tree walk
  optimizations at the middle level, and machine-specific optimizations lower
  down, \Treebeard{} can specialize inference code for each model on each
  supported hardware target. \Treebeard{} combines several novel optimizations
  at various abstraction levels to mitigate architectural bottlenecks and enable
  SIMD vectorization of tree walks.

  We implement \Treebeard{} using the MLIR compiler infrastructure and
  demonstrate its utility by evaluating it on a diverse set of benchmarks.
  \Treebeard{} is significantly faster than state-of-the-art systems, XGBoost
  and Treelite: by 2.6$\times$ and 4.7$\times$ respectively in a single-core
  execution setting, and by 2.3$\times$ and 2.7$\times$ respectively in
  multi-core settings.

\end{abstract}

  %generated by techniques like gradient boosting and random forests.

  % (run repeatedly on billions of data items).
 % such as tree tiling, tree walk unrolling, and tree walk interleaving.
 % Experimental evaluation demonstrates that \Treebeard{} optimizations
  % improve average latency over a batch of inputs by 2.2$\times$ over our baseline version.
 %% other frameworks like

### 2022-04-25 docs/MICRO 2022/introduction.tex
Micro paper (#37)
* Add results for multiple batch sizes run

* Changes to benchmark code

* Add xgboost and treelite compare results

* Add AMD results

* Add parallel performance results

* code to generate graphs + modified result numbers

* Fix bug in plotting code

* Add grid to line graphs

* Add grid lines

* Add results for varying number of cores

* Run parallel tests

* Add AMD parallel results

* Update graph generator

* Add scaling results for AMD

* Fix images, alter font sizes and axes

* Just use Probability based tiling

* Update images - Change axis font size, fix wrong graph

\section{Introduction}
% Decision trees are among the most widely used ML models. Cite Kaggle and looking glass 
Decision tree ensembles are one of the most popular classes of machine learning models \cite{KaggleSurvey,LookingGlass}.
They are generated by machine learning techniques like gradient boosting and random forests. 
The Kaggle state of data science and machine learning survey \cite{KaggleSurvey} shows that 
these are the most widely used classes of models among data scientists. An analysis of 
several machine learning pipelines that are in production use in a real large scale web company showed that 
gradient boosting machines and random forests were the two most widely used ML algorithms in the company \cite{LookingGlass}.
Not only are decision tree based models widely used, they are also used in a diverse set of 
applications\cite{DecisionTreesOverview}. GBM models were used in the CERN large hadron collider
to classify particles based on the data collected from the collider\cite{LHCModel}. Other applications 
include search engines\cite{YahooSearch}, prediction of the financial performance of companies\cite{Finance},
medical diagnostics\cite{Med1, Med2} and recommendation and notification systems\cite{Facebook}.

% Decision tree ensemble overview
Each node of a decision tree has a threshold value $v$ and a feature index (or column index) $i$.
To compute the prediction of a decision tree on an input row $x$\footnote{An input row is a
vector of numbers.}, a path from the root to leaf is computed. At a node, if $x_i < v$, then 
the walk moves to the left child. If not, we move to the right child. When a leaf is reached, 
the value of the leaf is returned as the prediction of the tree. 
Most ML techniques combine several decision trees into a forest (or ensemble) to improve prediction accuracy.
To compute the prediction of the forest, the prediction of each tree is computed and these predictions are 
then combined (usually by adding them).

% Inference on decision trees is hard 
% Pointer chasing -- cache performance, branch prediction, dependency stalls, not easy to vectorize
Given the wide spread use of decision tree ensembles, the ability to perform both high throughput and low latency inference is important.
\TODO{AP Since we don't talk about latency or throughput explicitly, should we be saying this?}
However, the tree walks required for inference are not straight-forward to optimize on a modern CPU. 
Firstly, naively implemented tree walks have poor spatial and temporal locality and therefore poor cache performance \cite{FAST,MilindTreeVectorization}.
Additionally, since the decision of which node to evaluate next can only be made after evaluating the current node,
true dependencies between instructions cause several pipeline stalls. Also, using SIMD instructions to accelerate 
tree walks is extremely challenging \cite{MilindTreeVectorization}.

Several systems like XGBoost\cite{XGBoost}, LightGBM\cite{LightGBM} and Sklearn\cite{Sklearn} implement
decision tree ensemble inference. These are libraries and implement some optimizations. However, these optimizations are hand
coded and need to be manually rewritten or redesigned for every target that is supported. Also, these 
systems cannot apply specialize inference code depending on the model. A compiler based approach is 
needed to address these problems. However, existing compilers only support fixed code generation techniques\cite{Treelite}.
To fill the need for an extensible compiler infrastructure for decision forest ensembles, we design and 
build Treebeard\footnote{In J. R. R. Tolkein's The Lord of the Rings, Treebeard was the oldest of the Ents left in Middle-earth, an 
ancient tree-like being who was a ``shepherd of trees''.}, an optimizing compiler for decision tree ensemble inference.
Our motivations for building Treebeard are as follows. 
\begin{enumerate}
  \item Existing libraries \cite{XGBoost, Treelite, LightGBM, VPred} perform specific optimizations and are hard to maintain/upgrade as hardware evolves. 
  Additionally, they cannot tailor inference code to the model being used. Past work has identified that the optimizations required change with the model
  and architectural parameters like cache size\cite{CacheConscious1, CacheConscious2, VPred}. 
  \item The repeated effort to optimize and maintain libraries on several targets is prohibitive. The proliferation of new architectures
  further exacerbates this problem. Compilers have been successful in alleviating this problem in other domains\cite{Halide, TVM}.
  However, no such compiler infrastructure currently exists for decision tree ensembles.
  \item Currently, no system exists that allows a thorough exploration of the potential optimization space for decision tree ensemble inference. 
  Compilers have been successful in addressing this problem with ML models like DNNs \cite{TVM, Tiramisu, XLA}. However, compiler techniques for
  decision tree ensembles are less well studied.
\end{enumerate}

We make the following contributions.
\begin{enumerate}
  \item We design and build Treebeard, an extensible compiler infrastructure for decision tree model inference. The 
  infrastructure is built to allow exploration of optimization and code generation techniques. \TODO{Is this claim too grand?}
  \item We develop a general infrastructure for the vectorization of decision tree walks based on grouping tree nodes into ``tiles''.
   This includes general support for code generation and the in-memory representation of tiled trees. The infrastructure can be 
   used to tile trees based on different cost functions.
  \item We show that trees can be tiled using different cost functions. We present two novel tiling methods that are implemented
  using the general tiling infrastructure. 
  \item We design and implement various model and loop transformations that significantly improve generated inference code performance 
  to show the power of the proposed framework.
\end{enumerate}

>>>>

\section{Introduction}
\label{sec:intro}
Decision tree ensembles are among the most popular classes of machine learning (ML) models~\cite{KaggleSurvey,LookingGlass}. The Kaggle state of ML survey 2021 \cite{KaggleSurvey} shows that 
more than 70\% of data scientists use decision tree ensembles while less than 40\% use neural networks. 
Such ensembles are generated by ML techniques like gradient boosting and random forests, reported to be the top
two algorithms used in production pipelines at a large scale web company\cite{LookingGlass}. Such models also 
have many diverse use cases\cite{DecisionTreesOverview}. Not only are they used in computer science applications 
like search~\cite{YahooSearch}, recommendation and notification systems\cite{Facebook}, but also in 
financial~\cite{Finance} and medical~\cite{Med1, Med2} applications. Gradient boosted models (GBM) are
even used in the CERN large hadron collider to classify particles\cite{LHCModel}.

\CommentOut{
Decision tree ensembles simply aggregate predictions made by a set of decision trees.
To compute the prediction of a decision tree on an input row $x$\footnote{An input row is a
vector of numbers.}, a path from the root to leaf is traversed.
Each node of a decision tree has a threshold value $v$ and a feature index $i$.
At a node, if $x_i < v$, then
the walk moves to the left child. If not, it moves to the right child. When a leaf is reached,
the value of the leaf is returned as the prediction of the tree.

%Most decision tree-based techniques combine several trees into a forest (or ensemble) to improve prediction accuracy.
%The prediction of each tree is computed and these predictions are 
%then combined (usually by adding them). 
}

A recent survey~\cite{SageMaker} that breaks down the cost of ownership of a
data science solution among different stages indicates that inference costs
have now become the dominant (in the range 45\%-65\%) component~\cite{Hummingbird}. This motivates
a careful study of the efficiency of inference with decision tree ensembles.
Such inference involves a simultaneous traversal of multiple decision trees.
Given an input row, a path from the root to leaf is traversed for each tree and
the values at the leafs are aggregated together to produce a prediction.  At
each internal node an input feature $x_i$ is compared with a threshold value $v$ for that node
to determine whether the walk moves left or right\footnote{  
The condition $x_i<v$ is the \emph{node predicate} or the \emph{node condition}.
At each node, if the node predicate is true, then
the walk moves to the left child. If not, it moves to the right child. When a leaf is reached,
the value $v$ of the leaf is returned as the prediction of the tree.}.

Optimizing tree walks on a CPU is challenging because they have irregular access
patterns and are sensitive to various architectural parameters.  A profile of a
basic traversal shows that a na\"ively implemented tree walk has poor spatial
and temporal locality, and therefore poor cache performance~\cite{FAST,MilindTreeVectorization}.  Frequent branching and true dependencies
between instructions cause several pipeline stalls. Furthermore, accelerating tree
walks with low level optimizations like vectorization using SIMD instructions is
extremely challenging~\cite{MilindTreeVectorization}.

Today, the most popular systems for performing inference for tree-based models
are libraries like XGBoost\cite{XGBoost}, LightGBM\cite{LightGBM} and
Sklearn\cite{Sklearn}.  As one would expect, these libraries implement a fixed
set of optimizations for the hardware configurations they support. As hardware
evolves, specializing the library to newer generations gets prohibitively
expensive and usually has a high lead time. Further, these libraries do not
specialize inference to the specifics of the model being used for inference.

Recent research has seen the advent of optimizing compilers for deep neural
networks~\cite{Halide, TVM, TensorComprehensions, Tiramisu, XLA}. Such compilers
have been shown to perform much better than domain-specific libraries in several
cases.  Surprisingly, despite their widespread usage, very few compilers exist
for decision tree ensembles~\cite{Treelite, Hummingbird}.  One 
system, Hummingbird~\cite{Hummingbird} builds on the success of DNN compilers by
transforming decision tree traversals to tensor operations. However, it sometimes
introduces more expensive operations like matrix multiplication
just to be able to leverage compilers
like TVM~\cite{TVM} for efficient code generation. As their results indicate,
when it comes to tree-based models this strategy does not always succeed: some
benchmarks' performance degrades when compared to a state-of-the-art library. 
Treelite\cite{Treelite}, the only other compiler for tree inference, uses 
a simple compilation strategy. It aggressively expands all trees in the 
model into \op{if-else} statements. As we show later in the paper, this strategy
is quite limited in applying various optimizations.

This paper presents the design and implementation of \Treebeard{}\footnote{In 
J. R. R. Tolkein's The Lord of the Rings, Treebeard was the oldest of the Ents left in Middle-earth, an 
ancient tree-like being who was a ``shepherd of trees''.}, an extensible optimizing compiler infrastructure for decision tree ensemble
inference. \Treebeard{} enables three different classes of optimizations: (i) pertaining to the nature of the algorithm, i.e., simultaneous traversal of several trees.
(ii) pertaining to the properties of the tree being traversed, like imbalances in structure and probabilities of reaching leaves. 
(iii) targeting the characteristics of the CPU, like support for vector instructions. 
We carefully construct the compiler so that different optimizations are applied at different intermediate
representations of the computation. By doing so, \Treebeard{} facilitates the selection and composition of
several optimizations at each level of abstraction, as well as automatic and efficient code generation.

We implement \Treebeard{} using the MLIR compiler infrastructure\cite{MLIR} and evaluate it 
on a diverse set of decision tree-based models. We report that the code generated by
\Treebeard{} is significantly faster than state-of-the-art systems: it is on average
$2.6\times$ and $4.7\times$ faster than XGBoost and Treelite respectively on a single core. 
Even with a very simple parallelization strategy, \Treebeard{} achieves speedups of $2.3\times$ and $2.7\times$
compared to XGBoost and Treelite on a 16-core system.
% \TODO{kr: is the below line needed}.
% Our optimizations improve performance significantly over a simple \Treebeard{} generated baseline (with comparable single-core performance as XGBoost but better than treelite) 
% on both Intel (by $2.2\times$) and AMD (by $1.8\times$) processors.

In summary, we make the following contributions.
\begin{enumerate}
\item We design and implement \Treebeard{}, an extensible compiler infrastructure for decision tree model inference. 
\Treebeard{} is built to allow exploration of several optimizations and code generation techniques. % \TODO{Is this claim too grand?}
\item We propose novel tiling transformations that reduce the cost of tree walks by grouping tree nodes into ``tiles''.
We propose tiling algorithms that can utilize specific properties of the model being compiled.
\item We design and implement various model and loop transformations that significantly improve generated inference
code performance. \Treebeard{} also enables parallelization of the inference computation.
\item We develop a general infrastructure for the vectorization of decision tree walks.
This includes general support for code generation and memory-layout optimizations for tiled trees.
\end{enumerate}

### 2022-04-25 docs/MICRO 2022/main.tex
Micro paper (#37)
* Add results for multiple batch sizes run

* Changes to benchmark code

* Add xgboost and treelite compare results

* Add AMD results

* Add parallel performance results

* code to generate graphs + modified result numbers

* Fix bug in plotting code

* Add grid to line graphs

* Add grid lines

* Add results for varying number of cores

* Run parallel tests

* Add AMD parallel results

* Update graph generator

* Add scaling results for AMD

* Fix images, alter font sizes and axes

* Just use Probability based tiling

* Update images - Change axis font size, fix wrong graph

\documentclass{sig-alternate}
\usepackage{mathptmx} % This is Times font
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\usepackage[hyphens]{url}
\usepackage[sort,nocompress]{cite}
\usepackage[final]{microtype}
\usepackage[keeplastbox]{flushend}
\usepackage{subfig}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
% Always include hyperref last
\usepackage[bookmarks=true,breaklinks=true,letterpaper=true,colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue]{hyperref}

@@

\lstdefinestyle{c++}{language=C++,
    morekeywords={ensemble, getTree, getRoot, isLeaf, isLeafTile, traverseTreeTile, getLeafValue, loadThresholds,
                  loadFeatureIndices, loadTileShape, getChildNode, parallel, InterleavedWalk, evaluateTilePredicates,
                  getChildTile, WalkDecisionTree},    
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{blue},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\scriptsize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

@@

%%%%%%%%%%%---SETME-----%%%%%%%%%%%%%
\title{Treebeard : An Optimizing Compiler for Tree Based ML Inference} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%% -- PAPER CONTENT STARTS-- %%%%%%%%
\input{abstract}
\input{introduction}
\input{overview}
\input{details}
\input{related}
%%%%%%% -- PAPER CONTENT ENDS -- %%%%%%%%

>>>>

\documentclass{sig-alternate}
\usepackage{mathptmx} % This is Times font
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{tabularx,booktabs}
\usepackage{multirow}
\usepackage[normalem]{ulem}
\usepackage[hyphens]{url}
\usepackage[sort,nocompress]{cite}
\usepackage[final]{microtype}
\usepackage[keeplastbox]{flushend}
%\usepackage{subfig}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{authblk}
% Always include hyperref last
\usepackage[bookmarks=true,breaklinks=true,letterpaper=true,colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue]{hyperref}

@@

\lstdefinestyle{c++}{language=C++,
    morekeywords={ensemble, getTree, getRoot, isLeaf, isLeafTile, traverseTreeTile, getLeafValue, loadThresholds,
                  loadFeatureIndices, loadTileShape, getChildTile, parallel, InterleavedWalk, evaluateTilePredicates,
                  getChildTile, WalkDecisionTree, moveToChildTile},
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{blue},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\scriptsize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2
}

@@

%%%%%%%%%%%---SETME-----%%%%%%%%%%%%%
\title{Treebeard : An Optimizing Compiler for Decision Tree Based ML Inference}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author[1]{Ashwin Prasad}
\author[2]{Sampath Rajendra}
\author[2]{Kaushik Rajan}
\author[1]{R Govindarajan}
\author[1]{Uday Bondhugula}
\affil[1]{Department of Computer Science And Automation, Indian Institute of Science}
\affil[2]{Microsoft Research}

%\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%

% \author{Ashwin Prasad}
% \affiliation{%
%  \institution{Indian Institute of Science}
%  \city{Bangalore}
%  \state{KA}
%  \country{India}}
% \email{ashwinprasad@iisc.ac.in}

% \author{
% % You can go ahead and credit any number of authors here,
% % e.g. one 'row of three' or two rows (consisting of one row of three
% % and a second row of one, two or three).
% %
% % The command \alignauthor (no curly braces needed) should
% % precede each author name, affiliation/snail-mail address and
% % e-mail address. Additionally, tag each line of
% % affiliation/address with \affaddr, and tag the
% % e-mail address with \email.
% %
% \alignauthor
% Ashwin Prasad\\
%       \affaddr{Indian Institute of Science, Bangalore}
%       \email{ashwinprasad@iisc.ac.in}
% \alignauthor
% Sampath Rajendra\\
%       \affaddr{Microsoft Research}
%        \email{srajendra@microsoft.com}
% \alignauthor
% Kaushik Rajan\\
%       \affaddr{Microsoft Research}
%        \email{krajan@microsoft.com}
% % \and
% \alignauthor
% R Govindarajan\\
%       \affaddr{Indian Institute of Science, Bangalore}
%       \email{govind@iisc.ac.in}
% \alignauthor
% Uday Bondhugula\\
%       \affaddr{Indian Institute of Science, Bangalore}
%       \email{udayb@iisc.ac.in}
% }

\renewcommand\Affilfont{\itshape\small}

@@

%%%%%% -- PAPER CONTENT STARTS-- %%%%%%%%
\input{abstract}
\input{introduction}
\input{overview}
\input{opts}
\input{results}
\input{related}
\input{conclusions}

%%%%%%% -- PAPER CONTENT ENDS -- %%%%%%%%
